Cybercrime and Online Video Games

### 2019-12-13 paper/paper.tex
Added bibliography start + start solutions

\subsubsection{Nuking or artificial lag}
The sub genre of hacks, as its name suggests, consists of artificially generating lag between the client and the server in order to gain an advantage. In some games, hits aren't registered until the server registeres a hit.

@@

\section{Solutions}
\subsection{Video Game Cheats}
[MIN 1 PARA PER OUR SOLUTIONS, EXPLAINING WHY ADDRESSES]

@@

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-base}

>>>>

\subsubsection{Nuking or artificial lag}
The sub genre of hacks, as its name suggests, consists of artificially generating lag between the 
client and the server in order to gain an advantage. In some games, hits aren't registered until 
the server registeres a hit. In this case, overloading the server with packets just enough to create lag
for every player on the server but not enough to cause the server to crash allows you to stall the game
enough for you to be able to win effortlessly in the next round.

@@

\section{Solutions}
\subsection{Video Game Cheats}
\subsubsection{Mirrored server design}

@@

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{paper}{}
